Towards planning of infantile cardiac surgery based on simulation

### 2012-02-27 Doc/Miccai/simulation.tex
miccai2012: few corrections
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@340 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

  \item[Subclavian flap aortoplasty:] The surgeon cuts the nearest artery,
    removing also half of the artery (along the axis) and part of the
    aorta in the affected place. He then uses the rest of the artery to
    patch the aorta.

@@

From our point of view the all these procedures share the same similarity:
parts of the circulatory system are sutured together or to a patch. These
parts are not too far away from each other. On this we have based our
general approach in the simulation.

The simple way how to perform the suturing would be to connect the
respective edges with springs. This approach however adds some unwanted
energy to the system. Our method is based solely on the relaxation of the
mesh of shell elements.

>>>>

  \item[Subclavian flap aortoplasty:] the nearest artery is cut,
    removing also half of the artery (along the axis) and part of the
    aorta in the affected place. He then uses the rest of the artery to
    patch the aorta.

@@

From our point of view the all these procedures share the same similarity:
parts of the circulatory system are sutured together or to a patch. These
parts are not too far away from each other. On this we have based our
general approach in the simulation. The simple way how to perform the
suturing would be to connect the respective edges with springs. This
approach however adds some unwanted energy to the system. Our method is
based solely on the relaxation of the mesh of shell elements.
